### 2014-12-12 paper.tex
Add compactness maps to paper

>>>>

  \begin{figure}
    \begin{center}
      \parbox{0.49\textwidth}{\centering \includegraphics[width=0.48\textwidth]{map-area_per.pdf} \\ Area vs. Perimeter}
      \parbox{0.49\textwidth}{\centering \includegraphics[width=0.48\textwidth]{map-convex_hull.pdf} \\ Convex Hull Area}
      \parbox{0.49\textwidth}{\centering \includegraphics[width=0.48\textwidth]{map-convex_hull_pop.pdf} \\ Convex Hull Population}
      \parbox{0.49\textwidth}{\centering \includegraphics[width=0.48\textwidth]{map-moment_area.pdf} \\ Moment of Area}
      \parbox{0.49\textwidth}{\centering \includegraphics[width=0.48\textwidth]{map-moment_pop.pdf} \\ Moment of Population}
      \parbox{0.49\textwidth}{\centering \parbox{0.4\textwidth}{\caption{Compactness of Pennsylvania districts as computed by various metrics.  Green is the most compact, and red is the least.\label{f:compactnessmaps}}}}
    \end{center}
  \end{figure}
